Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-14 manuscript/main.tex
back to proposition

Using this definition, the following lemma states that $\mathcal{U}$ is a compact operator under a mild condition.
	\begin{lemma}[Compactness condition] \label{lemma:compact_operator}

@@

The proof of Lemma \ref{lemma:compact_operator} is provided in Appendix \ref{section:proof:lemma:compact_operator}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{lemma:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
	\begin{proposition}\label{proposition: eigenanalysis}
		Under the condition of 
		\begin{equation*}
			\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle  W , \,  \xi \rangle_\mathcal{H}, Y \right)
		\end{equation*}
		is achieved when $\xi$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
	\end{proposition}
	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

	\section{Proof of Lemma \ref{lemma:compact_operator}}\label{section:proof:lemma:compact_operator}
\begin{proof}
	The brief strategy of the proof is as follows.
		We   show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous.
		Then we apply the Arzel\'{a}-Ascoli theorem to show that $\mathcal{U}$ is \textit{compact}.

>>>>

Using this definition, the following proposition states that $\mathcal{U}$ is a compact operator under a mild condition.
	\begin{proposition}[Compactness condition] \label{proposition:compact_operator}

@@

\end{proposition}
The proof of Proposition \ref{proposition:compact_operator} is provided in Appendix \ref{section:proof:proposition:compact_operator}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{proposition:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
\begin{proposition}[Existence of Maximizer for Covariance]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
	\begin{equation*} 
		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
		\end{equation*} 
	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
\end{proposition}
	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

	\section{Proof of Proposition \ref{proposition:compact_operator}}\label{section:proof:proposition:compact_operator}
\begin{proof}
	The brief strategy of the proof is as follows.
		We   show that an image of a bounded family in $\mathcal{H}$ under $\mathcal{U}$ is uniformly bounded and equicontinuous.
		Then we apply the Arzel\'{a}-Ascoli theorem to show that $\mathcal{U}$ is \textit{compact}.
